Effectiveness of community-based TURF-reserves in small-scale fisheries

### 2018-12-04 docs/paper/Villasenor-Derbez.Rmd
Added some caveats to the TURF-reserve paragraphs in the methods

TURFs are a fisheries management tool in which a well defined group of fishers have exclusive access to an explicitly delimited portion of the ocean. TURFs promote a sense of stewardship and incentivise resource users to sustainably manage their resources \citep{gelcich_2008,mccay_2017}. On the other hand, no-take marine reserves (marine reserves from hereinafter) are areas where all extractive activities are off-limits. These can be implemented to protect biodiversity but also as fishery management tools that restrict fishing effort and gears and therefore aid in the recovery of marine stocks. Commonly known as TURF-reserves, the combination of these tools increase the benefits of spatial access rights allowing the maintenance of healthy resources \citep{afflerbach_2014,lester_2017}.

Research on TURFs has shown that these areas have higher abundance of targeted species than sites operating under open access \citep{gelcich_2008,mccay_2014,mccay_2017}. Likewise, conservation science has shown how marine reserves lead to increased biomass, species richness, and abundance within the protected regions \citep{lester_2009-Ks,giakoumi_2017-V2,sala_2017-69}, and that these may have a series of additional benefits like climate change mitigation, protection from environmental variability, and fisheries benefits \cite{roberts_2017-J9,micheli_2012-EU,krueck_2017-J1}. The benefits resulting from reserves established within TURFs should be captured exclusively by the group of fishers with exclusive access. Although in theory these systems are successful \citep{costello_2010,smallhornwest_2018}, there is little empirical evidence of their effectiveness and the drivers of their success \citep{afflerbach_2014,lester_2017}.

>>>>

TURFs are a fisheries management tool in which a well defined group of fishers have exclusive access to an explicitly delimited portion of the ocean. They promote a sense of stewardship and incentivise resource users to sustainably manage their resources \citep{gelcich_2008,mccay_2017}. On the other hand, no-take marine reserves (marine reserves from hereinafter) are areas where all extractive activities are off-limits. These can be implemented to protect biodiversity but also as fishery management tools that restrict fishing effort and gears and therefore aid in the recovery of marine stocks. Commonly known as TURF-reserves, the combination of these tools should in theory increase the benefits of spatial access rights allowing the maintenance of healthy resources \citep{afflerbach_2014,lester_2017}.

Research on TURFs has shown that these areas have higher abundance of targeted species than sites operating under open access \citep{gelcich_2008,mccay_2014,mccay_2017}. Likewise, conservation science has shown how marine reserves lead to increased biomass, species richness, and abundance within the protected regions \citep{lester_2009,giakoumi_2017-V2,sala_2017-69}, and that these may have a series of additional benefits like climate change mitigation, protection from environmental variability, and fisheries benefits \cite{roberts_2017-J9,micheli_2012-EU,krueck_2017-J1}. The benefits resulting from reserves established within TURFs should be captured exclusively by the group of fishers with exclusive access. Although in theory these systems are successful \citep{costello_2010,smallhornwest_2018}, there is little empirical evidence of their effectiveness and the drivers of their success \citep{afflerbach_2014,lester_2017}.
